### 2020-12-08 fe_px_paper/Response_to_Reviewers.tex

\opening{Dear Dr. Benlliure,}

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in European Physical Journal A.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank  referee \#2 for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements. Referee \#1 had a number of comments which were either unhelpful, or factually inaccurate.  Nevertheless, their helpful suggestions were implemented, and responses to the remaining points are enclosed.

%   \colornote{Lee - should we make any comments about the hostility and unhelpful/incorrect comment from Reviewer 1 here?}

@@

 \pagebreak

 Referee \#1:

Authors have measured cross sections of the natFe(p,x), natCu(p,x) and natTi(p,x) reactions and done
model calculations using several codes with default parameters. No meaning of model calculations using
default parameter, author should adjust input parameter to fit experimental data.
It seems the paper related to measure cross sections for production of medical isotopes via proton
induced reactions on natFe, which play role to optimize production route; impurities, optimum energy
window, yield, etc. In this paper the above objects are not clearly presented. I would like to suggest to
calculate integral yields and discuss in details.
No meaning of the natCu(p,x) and natTi(p,x) reactions cross section measurements except monitor
reactions. Excitation functions of the monitor reactions induced on Cu and Ti should be determined and
compared with the IAEA recommended curve, which confirms experimental techniques and beam
parameters. Therefore, other reactions from Cu and Ti monitor should be omitted from the paper.

 \colornote{We thank the reviewer for their thoughtful comments, in particular the suggestion to add integral yield calculations.  All comments have been addressed below:}

@@

%   \colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole.}

Few more comments:

1. P-2, line-15, ‘...........our measured data to probe the role of angular momentum...’.It should
clear and details in discussion.

\colornote{Additional discussion of the implications of these results on the treatment of angular momentum in reaction modeling has been added throughout the paper. }

@@

2. Sample size 2.5 cm x2.5 cm is too large. What is the benefit of such sample size?

\colornote{Since the beam (approximately 8 mm diameter) is  much smaller than this, we operate our irradiation in the \enquote{underfilled} regime --- hence, we can use areal density to calculate the cross section. This standard approach minimizes any deviations from point geometry during the gamma assay of foils.  }

@@

3. The notifications ’25 MeV stack’ and ’55 MeV stack’ are not correct.

\colornote{Two separate irradiations were performed at incident proton energies of 25 and 55 MeV respectively. The stack design was described on page 2, line 37, and this process was described in the paragraph beginning on page 2, line 50. }

@@

4. Fig.1 is not special. Setup of 88-inch cyclotron is well characterized. The Fig. 1 should be
omitted.

\colornote{Per your suggestion, this figure has been removed.}

@@

5. In Fig.2, peak should be identified by energy and nuclide, not by symbol.

\colornote{This figure has been updated, replacing the legend with energy / decay mode / $E_\gamma$ for each decay line.}

@@

6. In Fig.3, why the trend of one stack is different from other.

\colornote{The abrupt change in the post-minimization value at the energies where the two individual stacks overlap can be attributed to the to the relatively large energy straggle at the back of the high energy stack. The \enquote{jump} between stacks in the old Fig. 3 /  new Fig. 2 arises from the fact that the stacks were exposed to a different integral fluence.}

@@

8. What is the meaning of value in bracket in Tables.

\colornote{Uncertainties are listed in the least significant digit (NDS Style), that is, 131.0(85)\,mb  means 131.0 $\pm$ 8.5\,mb. Clarification to this effect has been added to the caption of all tables.}

9. P-8, line 44, ‘The natFe, natCu and natTi(p,x)......’ is not proper writing.

\colornote{The language has been updated here to better distinguish these separate reaction groups.}

@@

\colornote{We would first like thank the reviewer for their  detailed summary and suggestions of the manuscript. It is clear that they read the manuscript thoroughly, and the feedback they have provided here has been vital for the improvement of the paper as a whole. All comments have been well-received, and implemented. }

@@

\begin{figure}
 \centering
 \includegraphics[width=0.7\textwidth]{./minimize_fluka_55.pdf}
 % sample_gspec.pdf: 489x257 pixel, 72dpi, 17.25x9.07 cm, bb=0 0 489 257
%  \caption{A gamma spectrum  from an activated Fe foil at approximately 55\,MeV (the maximum incident proton energy), collected 25 minutes after end-of-bombardment. Several observed reaction products are visible in this spectrum, and  the \ce{^{51}Cr} and \ce{^{52m}Mn} decay lines, which form two of the   primary reaction channels of interest, are  clearly isolated from surrounding peaks. }
%  \label{fig:gspec_femn}
\end{figure}

\colornote{Additionally, I removed the language in this section comparing the minimization results between AZ calculations and FLUKA, as well as Figure 4, which attempted to visually convey this, but I fear caused more confusion than it helped.  Most of the information needed is found in Figure 3B already, so this also helps avoid unnecessary duplication. Since we do not use the linear fit, AZ fluences estimates, or the FLUKA fluence model for any of our actual analysis,  having these in here might have partly led to the confusion.  Of all of this, only the FLUKA energy spectra (which lead to fluences when normalizing to IAEA monitor data) is actually used in our analysis, so I cut the rest to avoid any confusion in the final manuscript.  I hope that helps clarify things for you!}

The 55 MeV and 25 MeV irradiations have overlap: some energies are covered by both irradiations. This can be used to check the consistency of the methods used. However, the results do not clarify which results were obtained with which irradiation so that the reader cannot assert this consistency. Please, clearly specify which data were obtained from each of the two irradiations and show how consistent these are. A new plot or table may be necessary.

\colornote{This is a  very thoughtful suggestion. Running two overlapping stacks to build confidence through consistency was our goal for this, but the assignment of each foil to a stack is not clear, as you point out.  Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy. Additionally, the figure itself has an updated legend to clearly reflect this.}

@@

I strongly suggest creating three figures in the main text, one for each of the irradiate materials (i.e. take these out of the annex). They should support the discussion about the results. In principle, a discussion should follow the pattern: short statements about the comparison to earlier work by channel, short statements about the agreement with models by channel; overall agreement to earlier data and to particular models. Of course, a grouped approach can be taken (several channels of a given nature). Separate messages about the data and their agreement with model estimates from the potential use of the results. Usefulness of the results should be either in the introduction or in an outlook at the end. There is also where implications should be highlighted (outlook at the end of the paper).

\colornote{This is very important feedback! We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data. Your point that this new data warrants publication was very well-received, and we have added this new discussion to help show the importance of these results.}

Highlight clearly in the conclusions that model estimates are inadequate for even modest accuracy targets (like 20\%).

\colornote{We thank you for making this important point particularly clear. This point is a vital takeaway from this work, which was not made explicitly enough, but has now been more directly addressed in the conclusions.}

@@

If each activation foil is covered on both sides with kapton adhesive then this could be more clearly explained by either a drawing or the explicit mention of this in the tables describing the stacks.Please make this very explicit and mention clearly the best estimates for composition and thickness of these foils.

\colornote{The language in section 2.1 has been updated to reflect this, and a short statement to this effect has been added to the caption of Table 6.}

### 2020-12-08 fe_px_paper/fe_body_text.tex
Adding Lee's first part of comments

Manganese radionuclides are desirable for radiopharmaceutical applications, as 
% manganese is a 
% the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
% Manganese 
they possess well-established biochemistry, and have been 
% proven to be 
chelated 
% well 
by the complexing agent DOTA for tracking monoclonal antibodies with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immuno-PET applications, 
% with its rapid blood clearance 
offering the possibility for imaging within minutes of injection,
% \,\cite{Dong2015}.
% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
% making it more useful 
making it highly suitable for pre-clinical imaging as a longer-lived complement   to the more established immuno-PET agents \ce{^{89}Zr} and   \ce{^{64}Cu}.  
% Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long half-life and unfavorable high-energy decay gamma-rays 
% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
make it undesirable for clinical applications.
% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$~\pm~$0.2\,min)
% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
makes production and handling difficult, and with a  high-intensity gamma emission (1434.06\,keV, $I_\gamma = 98.2~\pm~0.5\%$),  
\ce{^{52m}Mn} is similarly undesirable for clinical applications\,\cite{Dong2015}.
% contributes significantly to patient dose\,\cite{Dong2015}.
% Another emerging manganese radionuclide is 
In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$~\pm~$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
% whose short lifetime makes it 
is more clinically suitable for rapid metabolic studies.
% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
% In addition, 
\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$~\pm~$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910~\pm~0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
% ,\cite{Wang2017}.

Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
% However, the m
Modeling of nuclear reactions in 
% this 
the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has
% performed a   measurement of 
measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on Fe.
% natural iron.
% This was carried out 
% in a
% using 
We used the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
% natural iron foils 
% iron 
Fe foils of natural isotopic abundance with 
% titanium 
Ti and 
% copper 
Cu monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work 
% seeks to 
complements 
% these measurements 
earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, 
% we are able to use a portion of the data we measured to gain insight into the role of 
we used our measured data to probe the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

@@

We constructed a pair of target stacks 
% were constructed 
for this work,
% , due to the large energy range desired to be spanned.
one stack covering the 55--20\,MeV range and the other  25--0\,MeV.
% , in order to 
This minimized the systematic uncertainties associated with significant degradation of beam energy, and
% In addition, the complementary  energy  of the  stacks helps build confidence  through 
included multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
% to build confidence in the results. 
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils 
% of each metal 
were cut down to 2.5$\times$2.5\,cm squares and spatially characterized 
% --- for each foil, length and width measurements were taken 
at four different locations using a digital caliper and micrometer (Mitutoyo America Corp.).
% , thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and 
Four mass measurements were performed using an analytical balance 
% after cleaning the foils with isopropyl alcohol.
% Using these length, width, and mass readings, the 
in order to determine their areal density. 
% and its uncertainty 
% (in mg/cm$^2$).
% for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were  sealed into \enquote{packets} between two pieces of  3M 5413-Series Kapton polyimide film tape,  
each piece of tape 
consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Plates of 6061 aluminum alloy  served as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy and mounts on the end of an electrically-isolated beamline.
The specifications of both target stacks 
% designs for this work are presented 
are in \autoref{tab:fe_stack_table} of 
% Appendix 
\ref{sec:fe_stack_design}.

\begin{figure}[ht]
 \centering
 \includegraphics[width=0.45\textwidth]{./figures/SAM_2494.JPG}
 % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
 \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack.
%  , before it was mounted in the beamline. 
 The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
\end{figure}

@@

% \caption{Specifications of the  target stack design in the present work. The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}. At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}

@@

% A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EoB).}

@@

Both target stacks were 
% assembled and 
separately irradiated at the  Lawrence Berkeley National Laboratory  (LBNL)
% , using the 
88-Inch Cyclotron, a  K=140 sector-focused cyclotron \cite{7999622}.
The 25\,MeV stack was irradiated for 
% approximately 
20\,minutes at a nominal current of 100\,nA,  for an  integral current of 31.61\,nAh, measured using a current integrator on the electrically-isolated beamline. 
The 55\,MeV stack was irradiated for 
% approximately 
10\,minutes at a nominal current of 120\,nA,  for an  integral current of 20.78\,nAh. 
The beam current
% , measured using a current integrator on the electrically-isolated beamline, 
remained stable under these conditions for the duration of each irradiation.
The approximately 1\,cm-diameter proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
Following end-of-bombardment (EoB), each stack was removed from the beamline and disassembled.
All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 20\,minutes following the end of each irradiation.

@@

% For consistency, a
A single 
% detector was used in this measurement, an 
ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector was used to determine the activities in each target.
% The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector.
% , with a series of standard calibration sources used to determine energy and efficiency for each position.
The foils were counted  for 
% a period of 
4 weeks following 
% end-of-bombardment.
(EoB).
% , to accurately quantify all induced activities.
An example of one of the gamma-ray spectra collected 
% in such a fashion 
is shown in \autoref{fig:gspec_femn}.
% An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
% For all spectra collected, n
Net peak areas were fitted using the 
% gamma spectrometry analysis 
code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
% , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

% To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used here to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
% used in this work 
should all be consistent at each 
% energy 
position.
% Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
% Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
% % stack design, namely, the
% areal densities of the stack components. 
This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic uncertainties.
% in stack areal densities.
As in  our prior work, variance minimization treats the effective density of a sensitive set of stack components (such as degraders) as a free parameter in proton transport calculations, to optimize agreement with the IAEA-recommended charged particle monitor standards.
Across multiple iterations of these simulations, this parameter is uniformly varied to find the energy spectra for each foil which minimizes the standard deviation  of the multiple measurements of proton fluence in a stack compartment.
The lowest energy position of a stack is often chosen for this, as it is the most sensitive to perturbations of the transport calculations.
It is important to note that this technique does not imply that the measured density of the stack components is incorrect --- rather, it is used as a surrogate to correct for poorly-characterized stopping power and other systematic uncertainties.

@@

% \def\arraystretch{1.5}
\begin{table*}
 \caption{Default settings for the reactions codes}
 \label{tab:fe_defaults}
 \resizebox{\textwidth}{!}{%
\begin{tabular}{ c c c c}

>>>>

Manganese radionuclides are desirable for radiopharmaceutical applications, as 
% manganese is a 
% the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
% Manganese 
they possess well-established biochemistry, and have been 
% proven to be 
chelated 
% well 
by the complexing agent DOTA for tracking monoclonal antibodies with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immuno-PET applications, 
% with its rapid blood clearance 
offering the possibility for imaging within minutes of injection,
% \,\cite{Dong2015}.
% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
% making it more useful 
making it highly suitable for pre-clinical imaging as a longer-lived complement   to the more established immuno-PET agents \ce{^{89}Zr} and   \ce{^{64}Cu}.  
% Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long half-life and unfavorable high-energy decay gamma-rays 
% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
make it undesirable for clinical applications.
% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$~\pm~$0.2\,min)
% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
makes production and handling difficult, and with a  high-intensity gamma emission (1434.06\,keV, $I_\gamma = 98.2~\pm~0.5\%$),  
\ce{^{52m}Mn} is similarly undesirable for clinical applications\,\cite{Dong2015}.
% contributes significantly to patient dose\,\cite{Dong2015}.
% Another emerging manganese radionuclide is 
In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$~\pm~$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{PhysRevC.96.014613,Wang2017}), 
% whose short lifetime makes it 
is more clinically suitable for rapid metabolic studies.
% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
% In addition, 
\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$~\pm~$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910~\pm~0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
% ,\cite{Wang2017}.

Developing production of these radionuclides requires well-characterized cross section data, or predictive models when such data have not been measured.   
% However, the m
Modeling of nuclear reactions in 
% this 
the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs \cite{Bernstein2019a}, our group has
% performed a   measurement of 
measured the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on Fe.
% natural iron.
% This was carried out 
% in a
% using 
We used the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
% natural iron foils 
% iron 
Fe foils of natural isotopic abundance with 
% titanium 
Ti and 
% copper 
Cu monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work 
% seeks to 
complements 
% these measurements 
earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, 
% we are able to use a portion of the data we measured to gain insight into the role of 
we used our measured data to probe the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

@@

Two separate irradiations were performed at incident proton energies of 25 and 55 MeV, respectively.
We constructed a pair of target stacks 
% were constructed 
for this work,
% , due to the large energy range desired to be spanned.
one stack covering the 55--20\,MeV range and the other  25--0\,MeV.
% , in order to 
This minimized the systematic uncertainties associated with significant degradation of beam energy, and
% In addition, the complementary  energy  of the  stacks helps build confidence  through 
included multiple overlapping measurements between 20--25\,MeV as a consistency check between the stacks.
% to build confidence in the results. 
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils 
% of each metal 
were cut down to 2.5$\times$2.5\,cm squares and spatially characterized 
% --- for each foil, length and width measurements were taken 
at four different locations using a digital caliper and micrometer (Mitutoyo America Corp.).
% , thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and 
Four mass measurements were performed using an analytical balance 
% after cleaning the foils with isopropyl alcohol.
% Using these length, width, and mass readings, the 
in order to determine their areal density. 
% and its uncertainty 
% (in mg/cm$^2$).
% for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were  sealed into \enquote{packets} between two pieces of  3M 5413-Series Kapton polyimide film tape,  
each piece of tape 
consisting of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Plates of 6061 aluminum alloy  served as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box
% , seen in \autoref{fig:fe_target_stack}, 
is machined from 6061 aluminum alloy and mounts on the end of a beamline,  electrically-isolated  for the purposes of current monitoring.
The specifications of both target stacks 
% designs for this work are presented 
are in \autoref{tab:fe_stack_table} of 
% Appendix 
\ref{sec:fe_stack_design}.

% \begin{figure}[ht]
%  \centering
%  \includegraphics[width=0.45\textwidth]{./figures/SAM_2494.JPG}
%  % IMG_1975.JPG: 3264x2448 pixel, 72dpi, 115.15x86.36 cm, bb=0 0 3264 2448
%  \caption{\label{fig:fe_target_stack}Photograph of the assembled 25\,MeV target stack.
% %  , before it was mounted in the beamline. 
%  The proton beam enters through the circular entrance in the foreground, and the upstream stainless steel profile monitor (SS-5) is visible at the front of the stack.}
% \end{figure}

@@

% \caption{Specifications of the  target stack design in the present work. The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}. At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EOB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}

@@

% A 316 stainless steel foil is inserted at both the front and rear of each target stack as a monitor of the beam's spatial profile, by developing radiochromic film (Gafchromic EBT3) after end-of-bombardment (EOB).}

@@

Both target stacks were 
% assembled and 
separately irradiated at the  Lawrence Berkeley National Laboratory  (LBNL)
% , using the 
88-Inch Cyclotron, a  K=140 sector-focused cyclotron \cite{7999622}.
The 25\,MeV stack was irradiated for 
% approximately 
20\,minutes at a nominal current of 100\,nA,  for an  integral current of 31.61\,nAh, measured using a current integrator on the electrically-isolated beamline. 
The 55\,MeV stack was irradiated for 
% approximately 
10\,minutes at a nominal current of 120\,nA,  for an  integral current of 20.78\,nAh. 
The beam current
% , measured using a current integrator on the electrically-isolated beamline, 
remained stable under these conditions for the duration of each irradiation.
The approximately 1\,cm-diameter proton beam incident upon each stack's upstream stainless steel profile monitor had a maximum energy of either 25 or 55\,MeV, with an approximately 2\% energy width due to multi-turn extraction --- these energy profiles were used for all later analysis.
Following end-of-bombardment (EOB), each stack was removed from the beamline and disassembled.
All activated foils were transported to a counting lab for gamma spectrometry, which started approximately 20\,minutes following the end of each irradiation.

@@

% For consistency, a
A single 
% detector was used in this measurement, an 
ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector was used to determine the activities in each target.
% The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector.
% , with a series of standard calibration sources used to determine energy and efficiency for each position.
The foils were counted  for 
% a period of 
4 weeks following 
% end-of-bombardment.
EOB.
% , to accurately quantify all induced activities.
An example of one of the gamma-ray spectra collected 
% in such a fashion 
is shown in \autoref{fig:gspec_femn}.
% An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
% For all spectra collected, n
Net peak areas were fitted using the 
% gamma spectrometry analysis 
code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
% , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

% To correct for a spread in the apparent proton fluence, seen most strongly in rear stack positions, t
The \enquote{variance minimization} techniques utilized in our recent work and established by Graves \etal\ have been used here to reduce uncertainty in proton fluence assignments due to poorly-characterized stopping power\,\cite{Voyles2018a,Graves2016}.
This method is based on the assumption that the independent measurements of proton fluence from the different monitor reactions 
% used in this work 
should all be consistent at each 
% energy 
position.
% Assuming that the recommended monitor reaction cross sections and FLUKA-modeled energy distributions are both accurate, 
% Any residual disagreement in the  observed proton fluences is  primarily due to poorly-characterized stopping power in simulations or a systematic error in the 
% % stack design, namely, the
% areal densities of the stack components. 
This disagreement is minor at the front of the stack, but gets progressively worse as the beam travels through the stack, due to the compounded effect of systematic errors.
% in stack areal densities.
As in  our prior work, variance minimization treats the effective density of a sensitive set of stack components (such as degraders) as a free parameter in proton transport calculations, to optimize agreement with the IAEA-recommended charged particle monitor standards.
Across multiple iterations of these simulations, this parameter is uniformly varied to find the energy spectra for each foil which minimizes the standard deviation  of the multiple measurements of proton fluence in a stack compartment.
The lowest energy position of a stack is often chosen for this, as it is the most sensitive to perturbations of the transport calculations.
It is important to note that this technique does not imply that the measured density of the stack components is incorrect --- rather, it is used as a surrogate to correct for poorly-characterized stopping power and other systematic uncertainties.

@@

% \def\arraystretch{1.5}
\begin{table*}
 \caption{Default settings for the reactions codes}
 \label{tab:fe_defaults}
 \resizebox{\textwidth}{!}{%
\begin{tabular}{ c c c c c}
